%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Shivansh Dubey (https://ishivanshdb.netlify.app/)
%
% Original repository:
% https://github.com/ishivanshdb/
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Shivansh}{Dubey}{ \urlstyle{same}\href{https://ishivanshdb.netlify.app/}{https://ishivanshdb.netlify.app/}\\
\href{mailto:shivanshsd10@gmail.com}{shivanshsd10@gmail.com} | \href{tel:+918303557710}{8303557710}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/ishivanshdb}{\bf ishivanshdb} \\
LinkedIn://  \href{https://www.linkedin.com/in/ishivanshdb}{\bf ishivanshdb} \\
Twitter://  \href{https://twitter.com/ishivanshdb}{\bf @ishivanshdb} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Dr APJ Abdul Kalam Technical University}
\descript{Bachelor of Technology}
\location{BTech in Computer Science and Engineering}
2014 -2020 | CGPA: 7.78/10 \\
\sectionsep

\subsection{PVM Inter College}
\descript{Intermediate}
\location{2015 - 2016 | Percentage: 68.4\% }
\sectionsep

\subsection{St Francis High School}
\descript{High School}
\location{2013 - 2014 | Percentage: 83.83\% }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CORE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Core}
\textbullet{} Software Engineering  \textbullet{} Database\\ \textbullet{}  Agile Methodology  \textbullet{} Operating System\\ \textbullet{} Data Structures and Algorithms
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TECHNICAL SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}
 \textbullet{} HTML/CSS \textbullet{} JavaScript \textbullet{} React.JS \\
 \textbullet{} MySQL \textbullet{} SQL Server \textbullet{} Docker\\
 \textbullet{} Microsoft Azure Stack \textbullet{} Azure DevOps  \\
 \textbullet{} Microsoft Power Automate \textbullet{} GitHub  \\ \textbullet{} Power BI \textbullet{} \LaTeX\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OPERATING SYSTEM
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Operating System}
\textbullet{} Windows \\
\textbullet{} Linux \\ 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages}
\textbullet{} Hindi \\
\textbullet{} English \\ 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    HOBBIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hobbies}
\textbullet{} Cooking \\
\textbullet{} Reading Books \\ 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{MAQ Software}
\descript{| Software Engineer II }
\location{MARCH 2021 - Present | Noida, IN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Successfully developed and implemented a new front-end architecture using React.js, resulting in significant improvements: a 25\% increase in page load speed and a 15\% increase in user engagement.
\item Created Azure Data Lake pipelines within Azure Data Factory to efficiently extract and process data in alignment with business requirements.
\item Utilized Databricks to create SQL views and scripts, seamlessly integrating them into Azure pipelines.
\item Designed and developed a reusable component for future use, leading to a substantial 40\% reduction in development time for new projects.
\item Optimized components for maximum performance across various web-capable devices and browsers, leading to a notable 30\% increase in user engagement and a 10\% increase in revenue.
\item Addressed and resolved UI-related bugs and issues to ensure a seamless, user-friendly experience.
\item Developed unit test cases for React modules to ensure robust testing of the system's UI functionality.
\end{tightemize}
\sectionsep

\runsubsection{Career Milaap}
\descript{| Web Development Intern }
\location{SEPT 2020 – JAN 2021 | Noida, IN}
\begin{tightemize}
\item Contributed to the development of multiple React web-pages, showcasing a proficiency in React, HTML, CSS and JavaScript.
\item Designed and implemented reusable React components, optimizing code efficiency and promoting modular development practices.
\item Developed and maintained technical documentation for the front-end codebase, resulting in a 20\% reduction in onboarding times for new developers.
\end{tightemize}
\sectionsep

\runsubsection{I Prep Learning}
\descript{| Software Developemnt Intern}
\location{DEC 2019 - JUNE 2020 | Faridabad, Haryana}
\begin{tightemize}
\item Interned on the development team, contributing to an innovative software solution aimed at enhancing students' comprehension of complex technical concepts.
\item Played a key role in designing a dynamic tool for interactive learning, providing valuable support to empower students on their educational journey.
\item Worked on project documentation to present it to stakeholders and facilitate the onboarding process for new team members.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACHIEVEMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievement }
\runsubsection{Smart India Hackathon 2018 }
\descript{| Top 6/200}
\location{MARCH 2018 | Chandigarh, IN}
\textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Kisaan Avitra -}}  Developed an IoT-enabled Android application designed to provide farmers with real-time information about crop status for \textbf{Government of India}. 
\sectionsep

\runsubsection{All India Research Championship - 2019 }
\descript{| Top 5/100}
\location{AUG 2019 | Mumbai, IN}
Came fifth position in \textbf{All India Research Championship-2019 (aIRC’19) }organized by \textbf{IIT Mumbai}.  
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
